title

### 2013-02-04 paper.tex
fixed dollar sign

Based on the above prediction, overall water demand in the United States will increase by 5.66 billion gallons per day between 2013 and 2025. 
Multiplying by the average cost of de-salinization facilities ($14  million per billion gallons per day) noted above, it would cost \$79.24 billion to build enough de-salinization plants to meet this demand.

>>>>

Based on the above prediction, overall water demand in the United States will increase by 5.66 billion gallons per day between 2013 and 2025. 
Multiplying by the average cost of de-salinization facilities (\$14  million per billion gallons per day) noted above, it would cost \$79.24 billion to build enough de-salinization plants to meet this demand.
